Quantifying maternal reproductive output of chondrichthyan fishes

### 2024-05-27 rmds/figures-supp.Rmd
revisions

## Figures
```{r, fig.width = 12, fig.height = 10}
ggplot(data %>% filter(par_name %in% "m50")) +
  geom_point(aes(as.factor(Nsamples), conv_success, col = repro_freq, group = repro_freq)) + 
  geom_line(aes(as.factor(Nsamples), conv_success, col = repro_freq, group = repro_freq)) +
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))))) +
  scale_color_brewer(palette = "Spectral") + 
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Number of samples", y = "Convergence success (%)", title = "Model convergence") +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")
```
Figure S1. Convergance success of alternative logistic regression models fit (n = 300) for school shark and gummy shark.

```{r, fig.width = 12, fig.height = 10}
ggplot(data %>% filter(par_name %in% "m50")) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), rel_error, col = repro_freq, group = repro_freq)) +
  geom_line(aes(as.factor(Nsamples), rel_error, col = repro_freq, group = repro_freq)) + 
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  scale_color_brewer(palette = "Spectral") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))))) + 
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Sample size", y = "Mean % relative error", title = expression("Bias - Length at 50% maternity")) +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")

@@

```{r, fig.width = 12, fig.height = 10}
ggplot(data %>% filter(par_name %in% "c")) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), rel_error, col = repro_freq, group = repro_freq)) +
  geom_line(aes(as.factor(Nsamples), rel_error, col = repro_freq, group = repro_freq)) + 
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  scale_color_brewer(palette = "Spectral") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))))) + 
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Sample size", y = "Mean % relative error", title = expression("Bias - "~italic(P)[Max])) +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")

@@

```{r, fig.width = 12, fig.height = 10}
ggplot(data %>% filter(par_name %in% "m50")) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), abs_error, col = repro_freq, group = repro_freq)) +
  geom_line(aes(as.factor(Nsamples), abs_error, col = repro_freq, group = repro_freq)) + 
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  scale_color_brewer(palette = "Spectral") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))))) + 
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Sample size", y = "Mean % absolute relative error", title = expression("Accuracy - Length at 50% maternity")) +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")
```
Figure S4. Accuracy (per cent absolute error) in parameter estimates of $\hat{L'_{50}}$ using alternative logistic regression models. Each point reflects a mean value from 300 simulated data sets.

```{r, fig.width = 12, fig.height = 10}
ggplot(data %>% filter(par_name %in% "c")) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), abs_error, col = repro_freq, group = repro_freq)) +
  geom_line(aes(as.factor(Nsamples), abs_error, col = repro_freq, group = repro_freq)) + 
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  scale_color_brewer(palette = "Spectral") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))))) + 
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Sample size", y = "Mean % absolute relative error", title = expression("Accuracy - "~italic(P)[Max])) +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")
```
Figure S5. Accuracy (per cent absolute error) in parameter estimates of $\hat{P_{Max}}$ using alternative logistic regression models. Each point reflects a mean value from 300 simulated data sets. Note 2PLF-maturity and 3PLF-fixed methods both used pre-specified values for $P_{Max}$ and are identical. 
\newpage

```{r fig.width = 12, fig.height=7}
ggplot(data %>% filter(par_name %in% "m50", method_long %in% c("3PLF - estimated", "3PLF - fixed"))) +
  geom_hline(yintercept = 50, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), int_coverage, col = repro_freq, group = repro_freq)) +
  geom_line(aes(as.factor(Nsamples), int_coverage, col = repro_freq, group = repro_freq)) + 
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  scale_color_brewer(palette = "Spectral") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))))) + 
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Sample size", y = "% interval coverage", title = expression("Interval coverage - Length at 50% maternity")) +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")
```
Figure S6. Confidence interval coverage for $L'_{50}$ for 3PLF methods. Figure shows the percentage of simulations (n = 300) where the true parameter value fell within the 50% bootstrap confidence interval. 
\newpage

```{r fig.width = 12, fig.height=5}
ggplot(data %>% filter(par_name %in% "c", method_long %in% c("3PLF - estimated"))) +
  geom_hline(yintercept = 50, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), int_coverage, col = repro_freq, group = repro_freq)) +
  geom_line(aes(as.factor(Nsamples), int_coverage, col = repro_freq, group = repro_freq)) + 
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  scale_color_brewer(palette = "Spectral") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))))) + 
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Sample size", y = "% interval coverage", title = expression("Interval coverage - "~italic(P)[Max])) +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")
```
Figure S7. Confidence interval coverage for $P_{Max}$ for the 3PLF-estimated method. Figure shows the percentage of simulations (n = 300) where the true parameter value fell within the 50% bootstrap confidence interval. 
\newpage

@@

```{r fig.width = 12, fig.height = 10}
ggplot(data %>% filter(par_name %in% "r_0")) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), rel_error, col = repro_freq, group = repro_freq)) +
  geom_line(aes(as.factor(Nsamples), rel_error, col = repro_freq, group = repro_freq)) + 
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  scale_color_brewer(palette = "Spectral") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))))) + 
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Sample size", y = "Mean % relative error", title = "Bias - Reproductive Output") +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")
```
Figure S10. Bias (per cent relative error) in $R_{0}$ calculated using maternity parameters obtained from alternative logistic regression models. Each point reflects a mean value from 300 simulated data sets

```{r fig.width = 12, fig.height = 10}
  ggplot(data %>% filter(par_name %in% "r_0")) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), abs_error, col = repro_freq, group = repro_freq)) +
  geom_line(aes(as.factor(Nsamples), abs_error, col = repro_freq, group = repro_freq)) + 
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  scale_color_brewer(palette = "Spectral") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))))) + 
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Sample size", y = "Mean % relative absolute error", title = "Accuracy - Reproductive Output") +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")
```
Figure S11. Accuracy (per cent absolute error) in $R_{0}$ calculated using maternity parameters obtained from alternative logistic regression models. Each point reflects a mean value from 300 simulated data sets

>>>>

## Figures
```{r, fig.width = 12, fig.height = 10}
ggplot(data %>% filter(par_name %in% "m50")) +
  geom_point(aes(as.factor(Nsamples), conv_success, col = repro_freq, group = repro_freq, size = n_maternal), alpha = 0.5) +
  scale_color_brewer(palette = "Spectral") + 
  scale_size_continuous(breaks = c(10, 50, 250, 1250)) + 
  geom_line(aes(as.factor(Nsamples), conv_success, col = repro_freq, group = repro_freq)) +
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))), order = 1),
         size = guide_legend("No. maternal females")) + 
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Number of samples", y = "Convergence success (%)", title = "Model convergence") +
  theme(legend.box = "vertical", legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")

```
Figure S1. Convergance success of alternative logistic regression models fit (n = 300) for school shark and gummy shark.

```{r, fig.width = 12, fig.height = 10}
ggplot(data %>% filter(par_name %in% "m50")) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), rel_error, col = repro_freq, group = repro_freq, size = n_maternal), alpha = 0.5) +
  scale_color_brewer(palette = "Spectral") + 
  scale_size_continuous(breaks = c(10, 50, 250, 1250)) + 
  geom_line(aes(as.factor(Nsamples), rel_error, col = repro_freq, group = repro_freq)) + 
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))), order = 1),
         size = guide_legend("No. maternal females")) +  
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Sample size", y = "Mean % relative error", title = expression("Bias - Length at 50% maternity")) +
  theme(legend.box = "vertical", legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")

@@

```{r, fig.width = 12, fig.height = 10}
ggplot(data %>% filter(par_name %in% "c")) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), rel_error, col = repro_freq, group = repro_freq, size = n_maternal), alpha = 0.5) +
  scale_color_brewer(palette = "Spectral") + 
  scale_size_continuous(breaks = c(10, 50, 250, 1250)) + 
  geom_line(aes(as.factor(Nsamples), rel_error, col = repro_freq, group = repro_freq)) + 
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))), order = 1),
         size = guide_legend("No. maternal females")) +  
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Sample size", y = "Mean % relative error", title = expression("Bias - "~italic(P)[Max])) +
  theme(legend.box = "vertical", legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")

@@

```{r, fig.width = 12, fig.height = 10}
ggplot(data %>% filter(par_name %in% "m50")) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), abs_error, col = repro_freq, group = repro_freq, size = n_maternal), alpha = 0.5) +
  scale_color_brewer(palette = "Spectral") + 
  scale_size_continuous(breaks = c(10, 50, 250, 1250)) + 
  geom_line(aes(as.factor(Nsamples), abs_error, col = repro_freq, group = repro_freq)) + 
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))), order = 1),
         size = guide_legend("No. maternal females")) +  
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Sample size", y = "Mean % absolute relative error", title = expression("Accuracy - Length at 50% maternity")) +
  theme(legend.box = "vertical", legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")

```
Figure S4. Accuracy (per cent absolute error) in parameter estimates of $\hat{L'_{50}}$ using alternative logistic regression models. Each point reflects a mean value from 300 simulated data sets.

```{r, fig.width = 12, fig.height = 10}
ggplot(data %>% filter(par_name %in% "c")) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), abs_error, col = repro_freq, group = repro_freq, size = n_maternal), alpha = 0.5) +
  scale_color_brewer(palette = "Spectral") + 
  scale_size_continuous(breaks = c(10, 50, 250, 1250)) + 
  geom_line(aes(as.factor(Nsamples), abs_error, col = repro_freq, group = repro_freq)) + 
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))), order = 1),
         size = guide_legend("No. maternal females")) +  
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Sample size", y = "Mean % absolute relative error", title = expression("Accuracy - "~italic(P)[Max])) +
  theme(legend.box = "vertical", legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")

```
Figure S5. Accuracy (per cent absolute error) in parameter estimates of $\hat{P_{Max}}$ using alternative logistic regression models. Each point reflects a mean value from 300 simulated data sets. Note 2PLF-maturity and 3PLF-fixed methods both used pre-specified values for $P_{Max}$ and are identical. 
\newpage

```{r fig.width = 12, fig.height=7}
ggplot(data %>% filter(par_name %in% "m50", method_long %in% c("3PLF - estimated", "3PLF - fixed"))) +
  geom_hline(yintercept = 50, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), int_coverage, col = repro_freq, group = repro_freq, size = n_maternal), alpha = 0.5) +
  scale_color_brewer(palette = "Spectral") + 
  scale_size_continuous(breaks = c(10, 50, 250, 1250)) + 
  geom_line(aes(as.factor(Nsamples), int_coverage, col = repro_freq, group = repro_freq)) + 
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))), order = 1),
         size = guide_legend("No. maternal females")) +  
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Sample size", y = "% interval coverage", title = expression("Interval coverage - Length at 50% maternity")) +
  theme(legend.box = "vertical", legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")
```
Figure S6. Confidence interval coverage for $L'_{50}$ for 3PLF methods. Figure shows the percentage of simulations (n = 300) where the true parameter value fell within the 50% bootstrap confidence interval. 
\newpage

```{r fig.width = 12, fig.height=5}
ggplot(data %>% filter(par_name %in% "c", method_long %in% c("3PLF - estimated"))) +
  geom_hline(yintercept = 50, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), int_coverage, col = repro_freq, group = repro_freq, size = n_maternal), alpha = 0.5) +
  scale_color_brewer(palette = "Spectral") + 
  scale_size_continuous(breaks = c(10, 50, 250, 1250)) + 
  geom_line(aes(as.factor(Nsamples), int_coverage, col = repro_freq, group = repro_freq)) + 
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))), order = 1),
         size = guide_legend("No. maternal females")) +  
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Sample size", y = "% interval coverage", title = expression("Interval coverage - "~italic(P)[Max])) +
  theme(legend.box = "vertical", legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")

```
Figure S7. Confidence interval coverage for $P_{Max}$ for the 3PLF-estimated method. Figure shows the percentage of simulations (n = 300) where the true parameter value fell within the 50% bootstrap confidence interval. 
\newpage

@@

```{r fig.width = 12, fig.height = 10}
ggplot(data %>% filter(par_name %in% "r_0")) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), rel_error, col = repro_freq, group = repro_freq, size = n_maternal), alpha = 0.5) +
  scale_color_brewer(palette = "Spectral") + 
  scale_size_continuous(breaks = c(10, 50, 250, 1250)) + 
  geom_line(aes(as.factor(Nsamples), rel_error, col = repro_freq, group = repro_freq)) + 
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))), order = 1),
         size = guide_legend("No. maternal females")) +  
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Sample size", y = "Mean % relative error", title = "Bias - Reproductive Output") +
  theme(legend.box = "vertical", legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")
```
Figure S10. Bias (per cent relative error) in $R_{0}$ calculated using maternity parameters obtained from alternative logistic regression models. Each point reflects a mean value from 300 simulated data sets

```{r fig.width = 12, fig.height = 10}
ggplot(data %>% filter(par_name %in% "r_0")) +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), abs_error, col = repro_freq, group = repro_freq, size = n_maternal), alpha = 0.5) +
  scale_color_brewer(palette = "Spectral") + 
  scale_size_continuous(breaks = c(10, 50, 250, 1250)) + 
  geom_line(aes(as.factor(Nsamples), abs_error, col = repro_freq, group = repro_freq)) + 
  facet_grid(method_long ~ species + mesh_name_long, scales = "free_y") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))), order = 1),
         size = guide_legend("No. maternal females")) +  
  cowplot::theme_half_open() +
  panel_border() +
  background_grid() +
  labs(x = "Sample size", y = "Mean % relative absolute error", title = "Accuracy - Reproductive Output") +
  theme(legend.box = "vertical", legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")

```
Figure S11. Accuracy (per cent absolute error) in $R_{0}$ calculated using maternity parameters obtained from alternative logistic regression models. Each point reflects a mean value from 300 simulated data sets

```{r fig.width = 7, fig.height= 5.5}
data <- read_rds(here("data", "simulations-pivot.Rds")) %>% 
  filter(method_long %in% "3PLF - estimated")

ggplot() + 
  geom_point(data = data, aes(x = rel_error_c, y = rel_error_m50, fill = repro_freq, size = n_maternal), pch = 21, alpha = 0.5) +
  scale_size_continuous(breaks = c(2, 10, 50, 250, 1250)) + 
  scale_fill_brewer(palette = "Spectral") + 
  facet_grid( ~ species) + 
  guides(fill = guide_legend(title = bquote(atop(paste(plain("True "),italic(P)[Max]),("Reproductive frequency"))), order = 1), size = guide_legend("No. maternal females")) + 
  theme_bw() +
  theme(legend.box = "vertical", legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center") + 
  xlab(expression("% relative error "~hat(italic(P)[Max]))) +
  ylab(expression("% relative error "~hat(italic(L^"'")[50])))
```

Figure S12. Uncropped version of Figure 2. Bias (per cent relative error) in parameter estimates for $\hat{L'_{50}}$ and $\hat{P_{Max}}$ for the 3PLF maternity function with $P_{Max}$ estimated. Each point represents parameter estimates from one iteration of simulated data, including all combinations of variables. Simulations with longer reproductive cycles and fewer maternal females, were associated with higher bias in both parameters $\hat{L'_{50}}$ and $\hat{P_{Max}}$.

### 2024-05-27 rmds/figures.Rmd
revisions

```{r fig.width = 7, fig.height= 5.5}
data <- read_rds(here("data", "simulations-pivot.Rds"))

ggplot() + 
  geom_point(data = data, aes(x = rel_error_c, y = rel_error_m50, col = repro_freq)) +
  scale_color_viridis_d(option = "D", direction = 1) + 
  facet_grid(species~method_long) + 
  ylim(-30, 50) +
  guides(colour = guide_legend(bquote(atop(paste(plain("True "),italic(P)[Max]),("Reproductive frequency"))))) + 
  theme_bw() +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center") + 
  xlab(expression("% relative error "~hat(italic(P)[Max]))) +
  ylab(expression("% relative error "~hat(italic(L^"'")[50])))
```
Figure 2. Bias (per cent relative error) in parameter estimates for $\hat{L'_{50}}$ and $\hat{P_{Max}}$ for 3PLF methods. Each point represents parameter estimates from one iteration of simulated data. Bias tended to increase as the true underlying $P_{Max}$ decreased.
\
\
\newpage

@@

data %>% 
  filter(par_name %in% "c") %>% 
  filter(method_long %in% c("3PLF - estimated", "3PLF - fixed")) %>% 
  filter(mesh_name %in% "high") %>% 
  ggplot() +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), abs_error, col = repro_freq, group = repro_freq)) +
  geom_line(aes(as.factor(Nsamples), abs_error, col = repro_freq, group = repro_freq)) + 
  facet_grid(species ~ method_long) + 
  scale_color_brewer(palette = "Spectral") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))))) + 
  theme_bw() + 
  labs(x = "Sample size", y = "Mean % absolute relative error") +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")
```
Figure 3. Accuracy (per cent absolute error) in parameter estimates  of $\hat{P_{Max}}$ for 3PLF methods. Large sample sizes were needed to accurately estimate $\hat{P_{Max}}$ and accuracy decreased as the duration of the reproductive cycle increased. Each point reflects a mean value from 300 simulated data sets. 
\
\
\newpage

```{r fig.width = 7, fig.height= 5.5}
data %>% 
  filter(par_name %in% "m50", method_long %in% c("3PLF - estimated", "3PLF - fixed")) %>% 
  filter(mesh_name %in% "high") %>% 
  ggplot() +
  geom_hline(yintercept = 50, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), int_coverage, col = repro_freq, group = repro_freq)) +
  geom_line(aes(as.factor(Nsamples), int_coverage, col = repro_freq, group = repro_freq)) + 
  facet_grid(species ~ method_long, scales = "free_y") + 
  scale_color_brewer(palette = "Spectral") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))))) + 
  theme_bw() + 
  labs(x = "Sample size", y = "% interval coverage") +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")
```
Figure 4. Confidence interval coverage for $\hat{L'_{50}}$ for 3PLF methods (high selectivity scenarios). Figure shows the percentage of simulations (n = 300) where the true parameter value fell within the 50% bootstrap confidence interval.
\
\
\newpage

@@

read_rds(here("data", "simulations-summarised.Rds")) %>% 
  filter(!(method_long %in% "2PLF - maternity" & repro_freq %in% "1 (Annual)")) %>% 
  mutate(Nsamples_sel = fct_cross(factor(mesh_name, levels = c("low", "high")), as.factor(Nsamples))) %>% 
  filter(par_name %in% "r_0") %>% group_by(species, Nsamples_sel, repro_freq) %>% 
  slice_min(abs(rel_error)) %>% 
  ggplot() + 
  geom_tile(aes(x = as.factor(Nsamples_sel), y = repro_freq, fill = method_long)) + 
  scale_fill_viridis_d() + 
  guides(fill = guide_legend(title = "Method")) + 
  facet_wrap(~species, nrow = 1) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) + 
  labs(x = "Selectivity: Sample size", y = bquote(atop(italic(P)[Max],("Reproductive frequency")))) 
```
Figure 5. Performance of alternative maternity functions in minimising bias in calculations of $R_0$. The preferred method was that which minimised bias, $|\text{relative error}|$ across 300 simulated datasets. Note 2PLF-maternity (Annual) scenarios were excluded for this comparison.
\
\
\newpage

read_rds(here("data", "simulations-summarised.Rds")) %>% 
  filter(!(method_long %in% "2PLF - maternity" & repro_freq %in% "1 (Annual)")) %>% 
  mutate(Nsamples_sel = fct_cross(factor(mesh_name, levels = c("low", "high")), as.factor(Nsamples))) %>% 
  filter(par_name %in% "r_0") %>% group_by(species, Nsamples_sel, repro_freq) %>% 
  slice_min(abs_error) %>%
  ggplot() + 
  geom_tile(aes(x = as.factor(Nsamples_sel), y = repro_freq, fill = method_long)) + 
  scale_fill_viridis_d() + 
  guides(fill = guide_legend(title = "Method")) + 
  facet_wrap(~species, nrow = 1) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) + 
  labs(x = "Selectivity: Sample size", y = bquote(atop(italic(P)[Max],("Reproductive frequency")))) 
```
Figure 6. Performance of alternative maternity functions in accurately calculating $R_0$. The best performing method was that which minimised mean absolute error across 300 simulated datasets. Note 2PLF-maternity (Annual) scenarios were excluded for this comparison.
\
\newpage

>>>>

```{r fig.width = 7, fig.height= 5.5}
data <- read_rds(here("data", "simulations-pivot.Rds")) %>% 
  filter(method_long %in% "3PLF - estimated")

ggplot() + 
  geom_point(data = data, aes(x = rel_error_c, y = rel_error_m50, fill = repro_freq, size = n_maternal), pch = 21, alpha = 0.5) +
  scale_size_continuous(breaks = c(2, 10, 50, 250, 1250)) + 
  scale_fill_brewer(palette = "Spectral") + 
  facet_grid( ~ species) + 
  ylim(-30,50) +
  guides(fill = guide_legend(title = bquote(atop(paste(plain("True "),italic(P)[Max]),("Reproductive frequency"))), order = 1), size = guide_legend("No. maternal females")) + 
  theme_bw() +
  theme(legend.box = "vertical", legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center") + 
  xlab(expression("% relative error "~hat(italic(P)[Max]))) +
  ylab(expression("% relative error "~hat(italic(L^"'")[50])))
```

Figure 2. Bias (per cent relative error) in parameter estimates for $\hat{L'_{50}}$ and $\hat{P_{Max}}$ for the 3PLF maternity function with $P_{Max}$ estimated. Each point represents parameter estimates from one iteration of simulated data (n = 43,129), including all combinations of variables. Simulations with longer reproductive cycles and fewer maternal females were associated with higher bias in both parameters $\hat{L'_{50}}$ and $\hat{P_{Max}}$. Note: 42 data points were cropped to aid with data visualization (see Figure S12 for uncropped figure).\
\
\newpage

@@

data %>% 
  filter(par_name %in% "c") %>% 
  filter(method_long %in% c("3PLF - estimated", "3PLF - fixed")) %>% 
  filter(mesh_name %in% "high") %>% 
  ggplot() +
  geom_hline(yintercept = 0, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), abs_error, col = repro_freq, group = repro_freq, size = n_maternal), alpha = 0.5) +
  scale_size_continuous(breaks = c(10, 50, 250, 1250)) + 
  geom_line(aes(as.factor(Nsamples), abs_error, col = repro_freq, group = repro_freq)) + 
  facet_grid(species ~ method_long) + 
  scale_color_brewer(palette = "Spectral") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))), order = 1),
         size = guide_legend("No. maternal females")) + 
  theme_bw() + 
  labs(x = "Sample size", y = "Mean % absolute relative error") +
  theme(legend.box = "vertical", legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")
```

Figure 3. Accuracy (per cent absolute error) in parameter estimates of $\hat{P_{Max}}$ for 3PLF methods. Large sample sizes were needed to accurately estimate $\hat{P_{Max}}$ and accuracy decreased as the duration of the reproductive cycle increased. Each point reflects a mean value from 300 simulated data sets.\
\
\newpage

data %>% 
  filter(par_name %in% "m50", method_long %in% c("3PLF - estimated", "3PLF - fixed")) %>% 
  filter(mesh_name %in% "high") %>% 
  ggplot() +
  geom_hline(yintercept = 50, linetype = "dashed") +
  geom_point(aes(as.factor(Nsamples), int_coverage, col = repro_freq, group = repro_freq, size = n_maternal), alpha = 0.5) +
  scale_size_continuous(breaks = c(10, 50, 250, 1250)) + 
  geom_line(aes(as.factor(Nsamples), int_coverage, col = repro_freq, group = repro_freq)) + 
  facet_grid(species ~ method_long, scales = "free_y") + 
  scale_color_brewer(palette = "Spectral") + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))), order = 1),
         size = guide_legend("No. maternal females")) + 
  theme_bw() + 
  labs(x = "Sample size", y = "% interval coverage") +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center") +
  theme(legend.box = "vertical", legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center")
```

Figure 4. Confidence interval coverage for $\hat{L'_{50}}$ for 3PLF methods (high selectivity scenarios). Figure shows the percentage of simulations (n = 300) where the true parameter value fell within the 50% bootstrap confidence interval.\
\
\newpage

```{r fig.width=7, fig.height= 4}
(p <- ggplot(data = data %>% 
  filter(method_long %in% c("3PLF - estimated"), par_name %in% "c"), aes(x = n_maternal, y = abs_error, col = repro_freq)) + 
  geom_point() + 
  scale_color_brewer(palette = "Spectral") +
  scale_y_continuous(breaks = seq(0, 90, 10)) +
  scale_x_continuous(breaks = seq(0, 1600, 200)) +
  facet_grid(~ species) + 
  guides(colour = guide_legend(bquote(atop(italic(P)[Max],("Reproductive frequency"))))) + 
  theme_bw() + 
  xlab("Median number of maternal females") + 
  ylab(expression("Mean % absolute error "~hat(italic(P)[Max]))) +
  theme(legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center") +
  theme(legend.box = "vertical", legend.position = "bottom", legend.direction = "horizontal", legend.justification = "center"))
```

Figure 5. Accuracy (per cent absolute error) in parameter estimates of $\hat{P_{Max}}$ for the 3PLF - estimated method as a function of number of maternal females. Each point reflects a value from 300 simulated data sets.\
\newpage

@@

read_rds(here("data", "simulations-summarised.Rds")) %>% 
  filter(!(method_long %in% "2PLF - maternity" & repro_freq %in% "1 (Annual)")) %>% 
  mutate(Nsamples_sel = fct_cross(factor(mesh_name, levels = c("low", "high")), as.factor(Nsamples))) %>% 
  filter(par_name %in% "r_0") %>% group_by(species, Nsamples_sel, repro_freq) %>% 
  slice_min(abs_error) %>%
  ggplot() + 
  geom_tile(aes(x = as.factor(Nsamples_sel), y = repro_freq, fill = method_long)) + 
  scale_fill_brewer(palette = "Spectral") + 
  guides(fill = guide_legend(title = "Method")) + 
  facet_wrap(~species, nrow = 1) +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) + 
  labs(x = "Selectivity: Sample size", y = bquote(atop(italic(P)[Max],("Reproductive frequency")))) 
```

Figure 6. Performance of four alternative maternity functions in accurately calculating $R_0$. The best performing method was that which minimised mean absolute error across 300 simulated datasets. Note 2PLF-maternity (Annual) scenarios were excluded for this comparison.\
\newpage
